Incremental Forward Reasoning for White-Box~Proof~Search

### 2025-02-25 paper.tex
Add some TODOs
Fix ordered partial application example

% TODO: standardise indices vs indexes
% TODO: standardise dots after equations
% TODO: rename variable maps to variable indices everywhere
% TODO: Title Case for paragraphs

@@

Note that matches represent only those partial applications where arguments are added without gaps.
Hence for a rule $r : A → B → C → D$, the applications $r~a~\_ : B \to D$ and $r~a~b : D$ for some $a : A$ and $b : B$ correspond to matches, but not $r~\_~b : A \to D$.
This prevents us from constructing $r~a~b$ in two different but ultimately redundant ways.
The term orders used in various saturation calculi have a similar effect.

>>>>

% TODO: standardise indices vs indexes
% TODO: standardise dots after equations
% TODO: rename variable maps to variable indices everywhere
% TODO: Title Case for paragraphs
% TODO: check over/underfull boxes
% TODO: ensure that numbers in evaluation discussion match the final data
% TODO: process Massin's minor feedback points

@@

Note that matches represent only those partial applications where arguments are added without gaps.
Hence for a rule $r : A → B → C$, the applications $r~a~\_ : B \to C$ and $r~a~b : C$ for some $a : A$ and $b : B$ correspond to matches, but not $r~\_~b : A \to C$.
This prevents us from constructing $r~a~b$ in two different but ultimately redundant ways.
The term orders used in various saturation calculi have a similar effect.
